Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-08 manuscript.tex
7 updates

When comparing the different RV estimates obtained from the mean of the Normal density, the mean or the median of the SN density, we see that in the case of real data, the amplitude of stellar activity is larger for the mean of the SN, followed by the median of the SN and the mean of the Normal. Although there is a huge gap between the first and the second estimate, the difference between the second and the third is much smaller. The mean of the SN density is therefore more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal, which is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.

>>>>

Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV, and then N mean RV. 
Although there appears to be a larger difference between the SN mean RV and the SN median RV, the SN median RV is similar to the N mean RV. 
Hence, the mean of the SN density appears to be more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal.  This is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not. \jessi{The previous sentence does not follow from the points made in the paragraph.}
